Generalized Plackett-Luce Likelihoods

### 2022-08-09 inst/jss_hyper3.Rnw
include an abstract

%% an abstract and keywords
\Abstract{
  The \code{hyper2} package is improved here to include \code{hyper3}
  objects.
}
\Keywords{Plackett-Luce, Bradley-Terry, Mann-Whitney}
\Plainkeywords{Plackett-Luce, Bradley-Terry, Mann-Whitney}

@@

\begin{figure}[htbp]
  \begin{center}
<<plotwilcoxlike,cache=TRUE>>=
a <- seq(from=0.02,to=0.8,len=40)
L <- sapply(a,function(p){loglik(p,Hxy)})
plot(a,L-max(L),type='b')
abline(h=c(0,-2))
abline(v=c(0.24))
abline(v=c(0.5),lty=2)
@
\caption{A\label{wilcox_likelihood} support for the Bradley-Terry
strength $p_a$ of permeability at term.  The evaluate of 0.24 is
shown; and the two-units-of support credible interval, which does not
exclude $H_0\colon p_a=0.5$ (dotted line), is also shown}
\end{center}
\end{figure}

@@

Above we see that Chopra threw the longest and second-longest throws
of 87.58m and 87.03 respectively; Vadlejch threw the third-longest
throw of 86.67m, and so on (\code{NA} entries correspond to
no-throws.)  Now convert the attempts table to a \code{hyper3} object,
again using function \code{attemptstable2supp3()} but this time pass
\code{give.supp=TRUE}:

>>>>

%% an abstract and keywords
\Abstract{

  The \code{hyper2} package furnishes extensive idiom to work with
  extensions of the Bradley-Terry probability model such as
  Plackett-Luce likelihood functions, team strengths, and reified
  entities (monsters).  Here, I present a generalization of
  \code{hyper2} in which multiple entities are constrained to have
  identical Bradley-Terry strengths.  A new \proglang{S3} class
  \code{hyper3}, along with associated methods, is motivated and
  introduced.  Four datasets are analysed, each analysis furnishing
  new insight, and each highlighting different capabilities of the
  package.
}
\Keywords{Plackett-Luce, Bradley-Terry, Mann-Whitney}
\Plainkeywords{Plackett-Luce, Bradley-Terry, Mann-Whitney}

@@

\begin{figure}[htbp]
  \begin{center}
<<plotwilcoxlike,echo=FALSE>>=
a <- seq(from=0.02,to=0.8,len=40)
L <- sapply(a,function(p){loglik(p,Hxy)})
plot(a,L-max(L),type='b')
abline(h=c(0,-2))
abline(v=c(0.24))
abline(v=c(0.5),lty=2)
@
\caption{A\label{wilcox_likelihood} support for the Bradley-Terry
strength $p_a$ of permeability at term.  The evaluate of 0.24 is
shown; and the two-units-of support credible interval, which does not
exclude $H_0\colon p_a=0.5$ (dotted line), is also shown}
\end{center}
\end{figure}

@@

Above we see that Chopra threw the longest and second-longest throws
of 87.58m and 87.03 respectively; Vadlejch threw the third-longest
throw of 86.67m, and so on (\code{NA} entries correspond to
no-throws.)  The attempts table may be converted to a \code{hyper3}
object, again using function \code{attemptstable2supp3()} but this
time passing \code{give.supp=TRUE}:
